Optimal (Multiway) Spatial Joins

### 2024-05-31 msj.tex
yufei
Computing R^*

>>>>

\extraspacing {\bf Computing $\bm{R^*_1, R^*_2, ..., R^*_{k-2}}$.} We consider, w.l.o.g., that each rectangle in the input $R_1 \cup ... \cup R_{k-2}$ is given a distinct integer ID in $[n]$. This allows us to create an array of size $n$ and allocate an array cell to each $r \in R_1 \cup ... \cup R_{k-2}$, with the property that the cell can be accessed by the ID of $r$ in constant time.

To compute $R^*_1, R^*_2, ..., R^*_{k-2}$, we start by deriving $\maxtop(r')$ for each rectangle $r'$ in $R'_1 \cup  ... \cup R'_{k-2}$. For this purpose, first initialize $\maxtop(r') = -\infty$ for each such $r'$. Recall that $r'$ is the trimmed rectangle of some rectangle $r$ in $R_1 \cup ... \cup R_{k-2}$. We store $\maxtop(r')$ in the array cell allocated to $r$.

Then, we scan $\J(R_1',...,R_{k-2}')$. For each tuple $\bm{t}$ therein, use $O(k)$ time to identify the rectangle $r' = \gbot(\bm{t})$, and then update in constant time $\maxtop(r')$ to the maximum between its current value and $\ytop(r')$. The scan requires $O(n + k \cdot \out)$ time.

Finally, for each $i \in [k-2]$, we construct $R_i^*$ by collecting the top-sliced rectangle (see definition in \eqref{eqn:hv:type1:topsliced}) of every rectangle $r' \in R_i'$ with $\maxtop(r') \neq -\infty$. This step takes $O(|R_i'|)$ time for each $i \in [k-2]$, or $O(n)$ total time for all $i$.
